05_DESeq_manipulation

### 2019-05-18 analysis/05_DESeq2_manipulate.Rmd
now with candidate genes

>>>>

## candidate genes

# make dataframe with geneids and names and counts
candidates <- cbind(geneinfo, countData)
candidates <- candidates %>%
  filter(grepl("OXT|AVP|POMC|PRKCZ|GRM|JUN", Name)) 
row.names(candidates) <- candidates$Name
candidates <- candidates %>% select(-row.names, -Name, -geneid, -entrezid)

#head(candidates)

candidates <- as.data.frame(t(candidates))
candidates$RNAseqID <- rownames(candidates)
#head(candidates)

candidates <- candidates %>% gather(gene, value, -RNAseqID)  %>% # https://tidyr.tidyverse.org/reference/gather.html
  filter(RNAseqID != "gene")
candidates$value <- as.numeric(candidates$value)
candidates$V1  <- candidates$RNAseqID
#head(candidates)

candidatecounts <- full_join(candidates, colData)
#head(candidatecounts)

candidatecounts$faketime <- as.numeric(candidatecounts$treatment)
#head(candidatecounts)

candidatecounts$gene <- as.factor(candidatecounts$gene)
levels(candidatecounts$gene)

p1 <- candidatecounts %>%
  filter(gene %in% c( "AVP", "AVPR1A", "AVPR1B", "AVPR2")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = eachgroup)
p1

print(p1)

p2 <- candidatecounts %>%
  filter(gene %in% c( "GRM2", "GRM4", "GRM5", "GRM7", "GRM8")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = eachgroup)
p2

print(p2)

p3 <- candidatecounts %>%
  filter(gene %in% c( "JUN", "JUND", "OXT", "POMC", "PRKCZ")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = eachgroup)
p3

print(p3)
